---
title: "02_data_munging_summarizing_R"
subtitle: Assignment
output:
  pdf_document: default
  html_document: default
---

Shreya Chandrasekharan
    
###**Problem 4**

####_Version Control_

1. Version control proves to be highly useful backing work up, forking and rewinding, and for collaborating.  
2. Even for the solo analyst, it comes in handy while backing up in different physical locations, while also accurately showing changes in subsequent backups.   Experimenting with data becomes an easier task since we can also revert to the last version of our work (branching).  
3. Version control immensely helps in perfecting reproducible research.  


```{r, echo=FALSE}
library(dplyr)
library(knitr)
library(magrittr)
library(tidyr)
library(beeswarm)
library(stargazer)
library(data.table)
library(lubridate)

```
   
###**Problem 5**   

```{r, echo=FALSE}
    ########################### 
    #Problem5_CMM_analysis  
    #get data  
    ########################### 

    url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/CMM.dat"
    CMM_raw<-read.table(url, header=F, skip=1, fill=T, stringsAsFactors = F)
    CMM_tidy<-CMM_raw[-1,]
    colnames(CMM_tidy)<-c("part","Op1_1","Op1_2","Op2_1","Op2_2")
    CMM_tidy<-CMM_tidy %>%  
        gather(op_rep,value,Op1_1:Op2_2) %>%  
        separate(op_rep,into=c("operator","replicate"),sep="_") %>%  
        mutate(operator = gsub("Op","",operator)) %>%  
        mutate(replicate = as.numeric(replicate)) %>%  
        mutate(part = as.numeric(part))
    ###########################
    
      knitr::kable(summary(CMM_tidy), caption="CMM data summary")
    
    ########################### 
    #Problem5_CMM_analysis  
    #plot  
    ###########################     
 boxplot(value~operator, data=CMM_tidy, xlab="Operator")
    beeswarm(value~operator, data=CMM_tidy, pwcol=CMM_tidy$replicate,pwpch=as.character(CMM_tidy$part),add=T)
    legend("topleft",legend = levels(as.factor(CMM_tidy$replicate)),pch=20,col=levels(as.factor(CMM_tidy$replicate)))
    
    ```

\newpage

####**Part (a): Sensory data**

```{r}
    ########################### 
    #Problem5_Sensory_analysis  
    #get data  
    ########################### 
    url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/Sensory.dat"
    Sensory_raw<-read.table(url, header=F, skip=1, fill=T, stringsAsFactors = F)
    Sensory_tidy<-Sensory_raw[-1,]
    Sensory_tidy_a<-filter(.data = Sensory_tidy,V1 %in% 1:10) %>%
                    rename(Item=V1,V1=V2,V2=V3,V3=V4,V4=V5,V5=V6)
    Sensory_tidy_b<-filter(.data = Sensory_tidy,!(V1 %in% 1:10)) %>%
                    mutate(Item=rep(as.character(1:10),each=2)) %>%
                    mutate(V1=as.numeric(V1)) %>%
                    select(c(Item,V1:V5))
    Sensory_tidy<-bind_rows(Sensory_tidy_a,Sensory_tidy_b)
    colnames(Sensory_tidy)<-c("Item",paste("Person",1:5,sep="_"))
    Sensory_tidy<-Sensory_tidy %>%  
        gather(Person,value,Person_1:Person_5) %>%  
        mutate(Person = gsub("Person_","",Person)) %>%
        arrange(Item)
    
    ########################### 
    

    knitr::kable(summary(Sensory_tidy), caption="Sensory data summary")
    ```

####**Part (b): Long Jump data**

```{r}

    ########################### 
    #Problem5_LongJump_analysis  
    #get data  
    ########################### 
    url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/LongJumpData.dat"
    LongJump_raw<-read.table(url, header=F, skip=1, fill=T, stringsAsFactors = F)
    colnames(LongJump_raw)<-rep(c("V1","V2"),4)
    LongJump_tidy<-rbind(LongJump_raw[,1:2],LongJump_raw[,3:4],
                             LongJump_raw[,5:6],LongJump_raw[,7:8])
    LongJump_tidy<-LongJump_tidy %>%  
        filter(!(is.na(V1))) %>%
        mutate(YearCode=V1, Year=V1+1900, dist=V2) %>%
        select(-V1,-V2)
    
    ########################### 
    

    knitr::kable(summary(LongJump_tidy), caption="Long Jump data summary")
```

####**Part (c): Brain vs Body data**
```{r}
    ########################### 
    #Problem5_BrainBody_analysis  
    #get data  
    ########################### 
    url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/BrainandBodyWeight.dat"
    BrainBody_raw<-read.table(url, header=F, skip=1, fill=T, stringsAsFactors = F)
    colnames(BrainBody_raw)<-rep(c("Brain","Body"),3)
    BrainBody_tidy<-rbind(BrainBody_raw[,1:2],BrainBody_raw[,3:4],
                             BrainBody_raw[,5:6])
    BrainBody_tidy<-BrainBody_tidy %>%  
        filter(!(is.na(Brain))) 
    
    ########################### 
    

    knitr::kable(summary(BrainBody_tidy), caption="Brain/Body weight data summary")
```

####**Part (d): Tomato data**
```{r}
    ########################### 
    #Problem5_Tomato_analysis  
    #get data  
    ########################### 
    url<-"http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/tomato.dat"
    Tomato_raw<-read.table(url, header=F, skip=2, fill=T, stringsAsFactors = F, comment.char = "")
    Tomato_tidy<-Tomato_raw %>%  
        separate(V2,into=paste("C10000",1:3,sep="_"),sep=",",remove=T, extra="merge") %>%
        separate(V3,into=paste("C20000",1:3,sep="_"),sep=",",remove=T, extra="merge") %>%
        separate(V4,into=paste("C30000",1:3,sep="_"),sep=",",remove=T, extra="merge") %>%
        mutate(C10000_3=gsub(",","",C10000_3)) %>%
        gather(Clone,value,C10000_1:C30000_3) %>%
        mutate(Variety=V1, Clone=gsub("C","",Clone)) %>%
        mutate(Variety=gsub("\\\\#"," ",Variety)) %>%
        separate(Clone,into = c("Clone","Replicate")) %>%
        select(-V1,Variety,Clone,value) %>%
        arrange(Variety) 
        
    ########################### 
    

    knitr::kable(summary(Tomato_tidy), caption="Tomato data summary")
```

###**Problem 6**

```{r echo=T, eval=F}

# Path to data
.datapath <- file.path(path.package('swirl'), 'Courses',
                      'R_Programming_E', 'Looking_at_Data',
                      'plant-data.txt')
# Read in data
plants <- read.csv(.datapath, strip.white=TRUE, na.strings="")

# Remove annoying columns
.cols2rm <- c('Accepted.Symbol', 'Synonym.Symbol')
plants <- plants[, !(names(plants) %in% .cols2rm)]

# Make names pretty
names(plants) <- c('Scientific_Name', 'Duration', 'Active_Growth_Period',
                   'Foliage_Color', 'pH_Min', 'pH_Max',
                   'Precip_Min', 'Precip_Max',
                   'Shade_Tolerance', 'Temp_Min_F')
```

####_Linear Model_
```{r, eval=FALSE}
my_lm <- lm(formula = Foliage_Color~pH_Min + pH_Max, data = plants)
my_lm


my_lm_anova <- anova(my_lm)
my_lm_anova
```
 
 _Comment:_
 There is an error in the above functions. 'Foliage_Color' is a Qualitative Attribute, whereas 'pH_Min' and 'pH_Max' are Numeric Variables. I was unable to test for a linear relationship between 'Foliage_Color' and a statistic that combines information in 'pH_Min' and 'pH_Max' or get ANOVA results using my current statistical knowledge. 
 
###**Problem 7** 

```{r, eval=FALSE}
    Car_Gebreken_raw <- read.csv("Open_Data_RDW__Gebreken.csv",stringsAsFactors = F, 
                                 nrows=200, header=T,quote = '"')
    Car_Geconstat_raw <- read.csv("Open_Data_RDW__Geconstateerde_Gebreken.csv", 
                                  stringsAsFactors = F, nrows=200, header=T)
    Car_Person_raw <- read.csv("Personenauto_basisdata.csv",stringsAsFactors = F,
                               nrows=200, header=T)
    
    Car_Gebreken_raw.colclass <- sapply(Car_Gebreken_raw,class)
    Car_Geconstat_raw.colclass <- sapply(Car_Geconstat_raw,class)
    Car_Person_raw.colclass <- sapply(Car_Person_raw,class)
    
    print("Gebreken")
    print(Car_Gebreken_raw.colclass)

    print("Geconstat")
    print(Car_Geconstat_raw.colclass)

    print("Personen")
    print(Car_Person_raw.colclass)
    
    #this had the defect code and description
     Car_Gebreken_select <- fread(input = "Open_Data_RDW__Gebreken.csv", 
                                  header = T, select=c(1,6), showProgress=F)
    #this has the license plate, inspection date and defect code
    Car_Geconstat_select <- fread(input = "Open_Data_RDW__Geconstateerde_Gebreken.csv", 
                                  
                                  header=T, select=c(1,3,5),showProgress=F)
    #this has the license plate, make and model of vehicle
    Car_Person_select <- fread(input = "Personenauto_basisdata.csv", 
                               header=T, showProgress = F, select = c(1,3,4))
    
    Car_Geconstat_select_2017 <-
      Car_Geconstat_select[grep("2017",
                                Car_Geconstat_select$"Meld datum door keuringsinstantie")]
    ########################### 
```    

```{r, eval=FALSE}    
    merge_License_plate <- merge(Car_Gebreken_select, Car_Geconstat_select,
                                 Car_Person_select, by="Kenteken")
    merge_Defect_code <- merge(Car_Gebreken_select,
                               Car_Geconstat_select, Car_Person_select, 
                               by="Gebrek identificatie")
    
    ```

_Comment:_
I have been unable to complete the tasks required under this problem. This goes on to show that I require more practice of R codes and also better online search skills for when I get stuck in problems.   
I hope to achieve computational efficiency with time, and be able to satisfactorily complete homework assignments at the very least. However, I aspire to be able to use the programming skills I am learning through this course for productive research work in the long run.
