---
title: "Homework 3"
author: "Shreya Chandrasekharan"
output:
  html_document: default
  pdf_document: default
---

---
title: "Homework 3"
output:
  pdf_document: default
  html_document: default
author: Shreya Chandrasekharan
---


```{r, echo=FALSE}
library(dplyr)
library(tidyr)
library(knitr)
library(ggplot2)
library(magrittr)
library(vioplot)
library(beeswarm)
library(stargazer)
library(data.table)
library(lubridate)

suppressMessages(library(dplyr))
suppressMessages(library(tidyr))
suppressMessages(library(knitr))
suppressMessages(library(ggplot2))
suppressMessages(library(magrittr))
suppressMessages(library(vioplot))
suppressMessages(library(beeswarm))
suppressMessages(library(stargazer))
suppressMessages(library(data.table))
suppressMessages(library(lubridate))

```

##**Problem 4**

###*_Programming Style Guides_*

_My Takeaway:_ Every person has their own style of programming their codes. The key is consistency in that style. Ultimately, mainting a consistent style of programming helps facilitate reproducible research, if the style improves the way the code can be interpreted.

I will try to add comments to my codes henceforth to improve my coding style. I will strive to be consistent with the way I define objects and functions.

##**Problem 5**

```{r, eval=FALSE} 
#Cannot run this code chunk, way too many markers
lint(filename = "C:/Users/Shreya/Desktop/STAT 5014/STAT_5014/HW2_Chandrasekharan_Shreya.Rmd")
```

_Some things I need to change in my code_
1. Spacing seems to be one of the most prominent markers.  I will need to start adding spaces after commas and around infix operators.
2. I will need to use only double-quotes as much as possible.
3.I will try not to cross 80 characters per line.

##**Problem 6**

```{r}
#Read the given data

data_rds <- 
    readRDS("C:/Users/Shreya/Desktop/STAT 5014/STAT_5014/03_good_programming_R_functions/HW3_data.rds")
mean.d1 <- data.frame()
mean.d2 <- data.frame()
sd.d1 <- data.frame()
sd.d2 <- data.frame()
cor.d12 <- data.frame()

#Set loop for mean, stamdard deviation, and correlation

for(i in 1:13){
    mean_dev1 <- mean(filter(data_rds, Observer == i)[, "dev1"])
    mean_dev2 <- mean(filter(data_rds, Observer == i)[, "dev2"])
    sd_dev1 <- sd(filter(data_rds, Observer == i)[, "dev1"])
    sd_dev2 <- sd(filter(data_rds, Observer == i)[, "dev2"])
    cor_dev1_dev2 <- cor(filter(data_rds, Observer == i)[, "dev1"], 
                         filter(data_rds, Observer == i)[, "dev2"])

    #Make one data table from many
    
    mean.d1 <- rbind(mean.d1, mean_dev1)
    mean.d2 <- rbind(mean.d2, mean_dev2)
    sd.d1 <- rbind(sd.d1, sd_dev1)
    sd.d2 <- rbind(sd.d2, sd_dev2)
    cor.d12 <- rbind(cor.d12, cor_dev1_dev2)
}

#Table

table_rds <- cbind(1:13, mean.d1, mean.d2, sd.d1, sd.d2, cor.d12)
colnames(table_rds) <- c("Observer", "Mean Dev1", "Mean Dev2", "SD Dev1",
                         "SD Dev2", "Correlation Dev1 Dev2" )
knitr::kable(table_rds, caption = "Observed Data")

#Boxplot

boxplot(mean.d1, mean.d2, xlab = "Mean Dev1", ylab = "Mean Dev2", main =  "Mean Boxplot")

#Violinplot

sd_plot_violin <- ggplot(table_rds, aes(x = sd.d1, y = sd.d2))
sd_plot_violin + geom_violin()

```

##**Problem 7**

```{r}
#Get link

BP_link <- "http://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/BloodPressure.dat"

#CHeck what's needed in data 

BP_raw <- read.table(BP_link, header = FALSE, skip = 2, fill = TRUE, 
                     stringsAsFactors = FALSE)

BP_tidy <- BP_raw[, -5]

#Column 5 is unneeded

#Change column names for clarity

colnames(BP_tidy) <- c("Day", "Device 1", "Device 2", "Device 3", "Doctor 1", 
                       "Doctor 2", "Doctor 3")

#Better presentation

knitr::kable(BP_tidy, caption = "Blood Pressure Measurement")


```

##**Problem 8**


\begin{equation} f(x) = 3^x - sin(x) + cos(5x) \end{equation}

```{r}

#Define function

newt_func <- function(fn, tol = 1E-18, x0 = 1, n = 20){
    h <- 0.001
    i <- 1
    x1 <- x0
    k <- n
    
#Try to reproduce what I saw online, pray it works

    while(i<=n){
        dx_func <- (fn(x0+h) - fn(x0))/h
    x1 <- (x0 - (fn(x0)/dx_func))
    k[i] < x1
    i <- i + 1
    if (abs(x1-x0) < tol) break
    x0 <- x1
    }
    return(k[1:(i + 1)])
}

fn <- function(x){3^x - sin(x) + cos(5*x)}
a <- newt_func(fn, x0 = 0, n = 5)
a

#It doesn't work :(

#The code looks like what it's "supposed" to look like (courtesy: A LOT of Google-ing).
#But I am not sure of what output I am getting.
```

    
##**Problem 9**

```{r, eval= FALSE}

#Oh no! Not this again!


    Car_Gebreken_raw <- read.csv("Open_Data_RDW__Gebreken.csv",stringsAsFactors = F, 
                                 nrows=200, header=T,quote = '"')
    Car_Geconstat_raw <- read.csv("Open_Data_RDW__Geconstateerde_Gebreken.csv", 
                                  stringsAsFactors = F, nrows=200, header=T)
    Car_Person_raw <- read.csv("Personenauto_basisdata.csv",stringsAsFactors = F,
                               nrows=200, header=T)
    
    Car_Gebreken_raw.colclass <- sapply(Car_Gebreken_raw,class)
    Car_Geconstat_raw.colclass <- sapply(Car_Geconstat_raw,class)
    Car_Person_raw.colclass <- sapply(Car_Person_raw,class)
    
    print("Gebreken")
    print(Car_Gebreken_raw.colclass)
 print("Geconstat")
    print(Car_Geconstat_raw.colclass)
    print("Personen")
    print(Car_Person_raw.colclass)
    
    #this had the defect code and description
     Car_Gebreken_select <- fread(input = "Open_Data_RDW__Gebreken.csv", 
                                  header = T, select=c(1,6), showProgress=F)
    #this has the license plate, inspection date and defect code
    Car_Geconstat_select <- fread(input = "Open_Data_RDW__Geconstateerde_Gebreken.csv", 
                                  
                                  header=T, select=c(1,3,5),showProgress=F)
    #this has the license plate, make and model of vehicle
    Car_Person_select <- fread(input = "Personenauto_basisdata.csv", 
                               header=T, showProgress = F, select = c(1,3,4))
    
    Car_Geconstat_select_2017 <-
      Car_Geconstat_select[grep("2017",
Car_Geconstat_select$"Meld datum door keuringsinstantie")]
   
```    

```{r, eval=FALSE}    
    merge_License_plate <- merge(Car_Gebreken_select, Car_Geconstat_select,
                                 Car_Person_select, by="Kenteken")
    merge_Defect_code <- merge(Car_Gebreken_select,
                               Car_Geconstat_select, Car_Person_select, 
                               by="Gebrek identificatie")
    ```

_CONFESSION:_ I tried and tried, and got nowhere with this particular question. I have simply copied what I had submitted in my previous homework, which itself was incorrect/incomplete. My biggest challenge still remains merging huge datasets.