---
title: "Homework 5"
author: "Shreya Chandrasekharan"
output:
  pdf_document: default
  html_document: default
---

```{r}

library(tidyr)
library(dplyr)
library(downloader)
library(data.table)
library(readr)
library(ggplot2)
library(fiftystater)
library(maps)
library(mapdata)

suppressMessages(library(tidyr))
suppressMessages(library(dplyr))
suppressMessages(library(downloader))
suppressMessages(library(data.table))
suppressMessages(library(readr))
suppressMessages(library(ggplot2))
suppressMessages(library(fiftystater))
suppressMessages(library(maps))
suppressMessages(library(mapdata))
```

##**Problem 3**

A good figure depends on whether or not it looks exactky the way it looks to others who see it, the way the researcher wanted them to visualize it. The objective for making the figure should be clear, its axes clearly labeled, while also being able to give the views an intuitive understanding of the data and convey the researcher's ideas. A ggood figure represents the underlying data in the "quickest and dirty" form.

##**Problem 4**

###**Part (a)**

#Proportion of successes

```{r, echo=FALSE}

prop_success <- function(vect) {
  
sum(vect)/length(vect)
}
```

###**Part (b)**

#Simulation of 10 coin flips

```{r}

set.seed(23456)
P4b_data <- matrix(rbinom(10, 1, prob = (30:40)/100), nrow = 10, ncol = 10)

```

###**Part (c)**

#Proportion of success in P4b_data

```{r, echo=FALSE}

#First, by column
prop_column <- apply(P4b_data, 2, FUN = prop_success)

#Then by row
prop_row <- apply(P4b_data, 1, FUN = prop_success)

```

####**_Comment_**: We observe the same proportion of success for coin flips across both columns and rows. This is because the data follows Binomial Distribution.

###**Part (d)**

#Matrix whose input is a probablility function that gives a vector whose elements are 10 flips of a coin as output 

```{r, echo=FALSE}

coin_func <- function(x) {
  rbinom(10, 1, x)
}

P4d1 <- (30:40)/100
P4d_data <- sapply(P4d1, coin_func)
print(P4d_data)

```

##**Problem 5**


```{r, echo=FALSE}

#Load data

data_url <-"http://www2.isye.gatech.edu/~jeffwu/book/data/starch.dat" 

starch_data <- read.table(data_url, header = TRUE, fill = TRUE, stringsAsFactors = FALSE)

#Exploratory analysis of data

summary(starch_data)

boxplot(thickness ~ starch, starch_data)
boxplot(strength ~ starch, starch_data)

#Correlations

cor(starch_data$thickness, starch_data$strength, method = "pearson")

#The respone variable is starch

starch_data_CA <- filter(starch_data, starch == "CA")
starch_data_CO <- filter(starch_data, starch == "CO")
starch_data_PO <- filter(starch_data, starch == "PO")

#Scatterplots by "starch"

par(mfrow=c(1,3))
plot(starch_data_CA$thickness, starch_data_CA$strength, main = "For CA")
plot(starch_data_CO$thickness, starch_data_CO$strength, main = "For CO")
plot(starch_data_PO$thickness, starch_data_PO$strength, main = "For PO")

```

##**Problem 6**

###**Part (a)**

#Get and import a database of US cities and states

```{r, echo=FALSE}

#we are grabbing a SQL set from here
#url_cities <- "http://www.farinspace.com/wp-content/uploads/us_cities_and_states.zip""

#download the files, looks like it is a .zip
    
download("http://www.farinspace.com/wp-content/uploads/us_cities_and_states.zip",

dest = "us_cities_states.zip")

unzip("us_cities_states.zip")
    
#read in data, looks like sql dump, blah
    
states <- fread(input = "./us_cities_and_states/states.sql",skip = 23,sep = "'", sep2 = ",", header = F, select = c(2,4))

cities <- fread(input = "./us_cities_and_states/cities.sql",skip = 23,sep = "'", sep2 = ",", header = F, select = c(2,4))

```

###**Part (b)**

```{r, echo=FALSE}

#Create a summary table of the number of cities included by state

city_num <- as.data.frame(table(unlist(cities$V4)))

colnames(city_num) <- c("State", "Number of Cities")

city_num

```

###**Part (c)**

```{r, echo=FALSE, eval=FALSE}

#Create a function that counts the number of occurances of a letter in a string

letter_count <- data.frame(matrix(NA,nrow=50, ncol=26))
    getCount <- function(letter, state){
      
      state_sub <- gsub(letter, "", state)
      return(nchar(state) - nchar(state_sub))
    }
    
        temp <- strsplit(state_name)
        
        return(count)

    for(i in 1:50){
        letter_count[i,] <- xx-apply()
    }

```

#Sorry, I didn't finish this question owing to my regression test. :(

###**Part (d)**

#Map!!

```{r, echo=FALSE, eval=FALSE}

#https://cran.r-project.org/web/packages/fiftystater/vignettes/fiftystater.html
    
    
data("fifty_states") # this line is optional due to lazy data loading
crimes <- data.frame(state = tolower(rownames(USArrests)), USArrests)
# map_id creates the aesthetic mapping to the state name column in your data
p <- ggplot(crimes, aes(map_id = state)) + 
# map points to the fifty_states shape data
geom_map(aes(fill = Assault), map = fifty_states)  
expand_limits(x = fifty_states$long, y = fifty_states$lat) +
      coord_map() +
      scale_x_continuous(breaks = NULL) + 
      scale_y_continuous(breaks = NULL) +
      labs(x = "", y = "") +
      theme(legend.position = "bottom", 
            panel.background = element_blank())
    
p

ggsave(plot = p, file = "HW5_Problem6_Plot_Chandrasekharan.pdf")
```
